### 2020-02-11 submission/all_models.tex
all updates

In this section, we summarize results from a large-scale analysis of hundreds of CV models, including models developed for image classification, segmentation, and a range of related tasks.  
Our aim is to complement the detailed results from Sections~\ref{sxn:cv} and~\ref{sxn:nlp} by providing broader conclusions. % about norm-based and PL-based metrics.
The models we consider have been pretrained on nine datasets, including ImageNet-1K, and CIFAR-10, CIFAR-100, Street View House Numbers (SVHN), Caltech-UCSD Birds-200-2011 (CUB-200-2011), Pascal VOC2012, ADE20K, Cityscapes, and Common Objects in Context (COCO). 
%%The pretrained models and their accuracy metrics are summarized in the osmr github~\cite{charles-add-link}.
We provide more details about our experimental setup in Appendix~\ref{sxn:appendix}.

@@

Our results are summarized in Table~\ref{table:results}.
For the mean, larger $R^{2}$ and smaller $MSE$ are desirable; and for the standard deviation, smaller values are desirable.
Taken as a whole, over the entire corpus of data, PL-based metrics are somewhat better for both the $R^{2}$ mean and standard deviation; and PL-based metrics are much better for $MSE$ mean and standard deviation.
These (and other) results suggest our conclusions from Sections~\ref{sxn:cv} and~\ref{sxn:nlp} hold much more generally, and they suggest ovbious questions for future work.

>>>>

In this section, we summarize results from a large-scale analysis of hundreds of CV models, including models developed for image 
classification, segmentation, and a range of related tasks.  
Our aim is to complement the detailed results from Sections~\ref{sxn:cv} and~\ref{sxn:nlp} by providing broader conclusions. % about norm-based and PL-based metrics.
The models we consider have been pretrained on nine datasets, shown in Table~\ref{table:datasets}.
%including ImageNet-1K, and CIFAR-10, CIFAR-100, Street View House Numbers (SVHN), Caltech-UCSD Birds-200-2011 (CUB-200-2011), Pascal VOC2012, ADE20K, Cityscapes, and Common Objects in Context (COCO). 
%%The pretrained models and their accuracy metrics are summarized in the osmr github~\cite{charles-add-link}.
We provide full details about how to reproduce these results in Appendix~\ref{sxn:appendix}.

@@

Our results are summarized in Table~\ref{table:results}.
For the mean, larger $R^{2}$ and smaller $MSE$ are desirable; and for the standard deviation, smaller values are desirable.
Taken as a whole, over the entire corpus of data, PL-based metrics are somewhat better for both the $R^{2}$ mean and standard deviation;
and PL-based metrics are much better for $MSE$ mean and standard deviation.
These (and other) results suggest our conclusions from Sections~\ref{sxn:cv} and~\ref{sxn:nlp} hold much more generally, and they suggest
obvious questions for future work.
